Reaching is Better When You Get What You Want: Realtime Feedback of Intended Reaching Trajectory Despite an Unstable Forces

### 2015-05-04 Paper2frontiers/frontiers.tex
updated for writing from home

\title[Running Title]{Reaching is Better When You Get What You Want: Realtime Feedback of Intended Reaching Trajectory Despite Turbulence}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
\topic{}% If your article is part of a Research Topic, please indicate here which.

@@

% For Original Research Articles, Clinical Trial Articles, and Technology Reports the introduction should be succinct, with no subheadings.
Humans often interact with uncertain and complicated environments, such as turbulence, crowds, and traffic. Despite our capacity to learn and adapt, some environments evolve too quickly or with too much uncertainty for meaningful learning. In such an environment, planning a specific might seem nonsensical. Instead, a continuous cycle of reaction to the environment seems intuitive. We recently developed an algorithm that could recover the path a person intended to take even if they were forced off that path by environmental disturbances \citep{horowitz2015determining}. Surprisingly, some subjects did not alter their intended even following exposure to unexpected pulses of force. If people continuously reacted to their environment, we should always see some response.

>>>>

\title[Running Title]{Reaching is Better When You Get What You Want: Realtime Feedback of Intended Reaching Trajectory Despite an Unstable Forces}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
\topic{}% If your article is part of a Research Topic, please indicate here which.

@@

% For Original Research Articles, Clinical Trial Articles, and Technology Reports the introduction should be succinct, with no subheadings.
Humans often interact with uncertain and complicated environments, such as turbulence, crowds, and traffic. Despite our capacity to learn and adapt, some environments evolve too quickly or with too much uncertainty for meaningful learning. In such an environment, planning a specific route might seem nonsensical. Instead, a continuous cycle of reaction to the environment with no specific intended route might seem more intuitive. We explore the counter-intuitive possibility that a specific route is constructed even when the environment is unstable and unpredictable.

If people try to achieve a goal while minimizing some measure of cost, it is possible to compute a set of rules for reacting to the environment without a specific intended path using optimal feedback control\citep{todorov2002optimal}. This modeling strategy is not necessarily a scientific hypothesis as a measure of cost can always be found \text{a posteriori} that reproduces the behaviors observed and no hypothesized cost function has been claimed as sufficient to describe all reaching. This   but they predict reaction to disturbance. We recently developed an algorithm that could recover the route a person intended to take even if they were forced off of it by environmental disturbances \citep{horowitz2015determining}. Surprisingly, some subjects did not alter their intended route even following exposure to unexpected pulses of force. If humans a plan a route, even if they might change that route in response to disturbance, can they use feedback? Is a route really what they want? Does it take learning?
